Title Text

### 2014-04-08 intromoa.tex
a few more updates for clarity
I added a few more sentences in the ONF paragraph to assist in clarity.
Again, take out whatever you wish.

Get shape: 
\begin{eqnarray}
\rho X & = & \rho (2 \take (\Phi A)) \nonumber \\
& = & 2 \cat ((1\drop (\rho ( \Phi A)))) \nonumber \\
&=& 2 \cat ((1 \drop (\rho  A))) \nonumber \\
&=& 2 \cat <\;5\;4> \nonumber \\
&=& <2\;4\;5>
\end{eqnarray}
Now that we have the {\em shape}, we can {Psi-Reduce}.
\[ \forall \;\;\; i,j,k \;\;\; \ni \;\;\; 0 \;\;\;\leq i,j,k < \;\;\;<2\;4\;5> \]
\[<i\;j\;k> \psi X \]
\begin{eqnarray}
& =&<i\;j\;k> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) \nonumber \\
&=&<j\;k> \psi (<i> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) )\nonumber \\
&= &<j\;k> \psi ((<i> \psi ( 2 \take (\Phi A))) \nonumber \\
&&\;\;\;\;\;\times ( <i> \psi ( 1 \drop (\Phi A)))) \nonumber \\
&= &<j\;k> \psi (( <i> \psi (\Phi A)) \times (<i+1> \psi (\Phi A))) \nonumber \\
&=&<j\;k> \psi ((<((\rho A)[0] - 1 - i)> \psi A ) \nonumber \\
&& \;\;\;\;\;\times  (<((\rho A)[0] - 1 -( i + 1))> \psi A ) )\nonumber \\
&=&<j\;k> \psi ((< 2-i> \psi A ) \times (<1-i>  \psi A) ) \nonumber \\
&=& (< (2-i)\; j\;k> \psi A )  \times (<(i-i) \; j\;k> \psi A ) 
 \end{eqnarray}
\normalsize
This is the DNF, or semantic normal form. To proceed further we must know more about the data, i.e. layout, and architecture. 
\subsection* {Applying the Psi Correspondence Theorem: PCT}
We now want to {\em transform} the DNF above to a {\em Generic} Operational Normal Form (ONF) or way 
to {\em build the code}.  The PCT~\cite{muljen94}, which generalizes the mapping function 
gamma, $\gamma$,   turns short indices into start, stops, and strides.
Note that we still use {\em Psi-Reduction} but now just on vectors.  
We start by analyzing the shape of the result in conjunction with the indicies involved
in the computation and observe that the indices for $j$ and $k$ are contiguous allowing
us to only use the primary axis index in the mapping.
Thus, let Y denote $(<2-i> \psi A ) \times ( <1-i> \psi A)$. Then the shape of Y, i.e.
\begin{eqnarray}
\rho Y= 1 \drop (\rho A) = 1 \drop <3\;5\;4> = <5\;4>
\end{eqnarray}
i.e. the bounds for $j$ and $k$  above.
Continuing with the PCT to create the {\em generic} ONF on p=2 processors, we use the index of the primary axis, i, $\ni\;\;0 \leq  i < p$, since $\rho X = <2\;4\;5>$.
Using $\gamma_{row}$ for row major ordering, Y is transformed into:
\small
\begin{eqnarray}
a[ (( \gamma(<2-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] \nonumber \\
\times a[ (( \gamma(<1-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] 
\end{eqnarray}
Reducing, we get
\begin{eqnarray}
a[ (( \gamma(<2-i >; <3>))) \times \pi ( <5\;4>)  + \iota \pi <5\;4> ] \nonumber \\
\times a[ (( \gamma(<1-i >; <3>))) \times \pi ( <5\;4>)   )  + \iota \pi <5\;4>  ]\nonumber \\
a[( (2-i) \times  20)  + \iota 20 ] \nonumber \\
\times a[( (i-1) \times 20 )  + \iota 20 ]
\end{eqnarray}
\normalsize
which transforms the indexing into start, stride, and stop, a universal hardware description and easiliy transformed
to the mnemonics used at any hardware level ~\cite{fftharry}.
We could add more dimensions to analyze prefetching, buffer sizes, vector registers, cache, etc.

>>>>

Get shape: 
\begin{eqnarray}
\rho X & = & \rho (2 \take (\Phi A)) \nonumber \\
& = & 2 \cat ((1\drop (\rho ( \Phi A)))) \nonumber \\
&=& 2 \cat ((1 \drop (\rho  A))) \nonumber \\
&=& 2 \cat <\;5\;4> \nonumber \\
&=& <2\;4\;5>
\end{eqnarray}
Now that we have the {\em shape}, we can {Psi-Reduce}.
\[ \forall \;\;\; i,j,k \;\;\; \ni \;\;\; 0 \;\;\;\leq i,j,k < \;\;\;<2\;4\;5> \]
\[<i\;j\;k> \psi X \]
\begin{eqnarray}
& =&<i\;j\;k> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) \nonumber \\
&=&<j\;k> \psi (<i> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) )\nonumber \\
&= &<j\;k> \psi ((<i> \psi ( 2 \take (\Phi A))) \nonumber \\
&&\;\;\;\;\;\times ( <i> \psi ( 1 \drop (\Phi A)))) \nonumber \\
&= &<j\;k> \psi (( <i> \psi (\Phi A)) \times (<i+1> \psi (\Phi A))) \nonumber \\
&=&<j\;k> \psi ((<((\rho A)[0] - 1 - i)> \psi A ) \nonumber \\
&& \;\;\;\;\;\times  (<((\rho A)[0] - 1 -( i + 1))> \psi A ) )\nonumber \\
&=&<j\;k> \psi ((< 2-i> \psi A ) \times (<1-i>  \psi A) ) \nonumber \\
&=& (< (2-i)\; j\;k> \psi A )  \times (<(i-i) \; j\;k> \psi A ) 
 \end{eqnarray}
\normalsize
This is the DNF, or semantic normal form. To proceed further we must know more about the data, i.e. layout, and architecture. 
\subsection* {Applying the Psi Correspondence Theorem: PCT}
We now want to {\em transform} the DNF above to a {\em Generic} Operational Normal Form (ONF) or way 
to {\em build the code}.  The PCT~\cite{muljen94}, which generalizes the mapping function 
gamma, $\gamma$,   turns short indices into start, stops, and strides.
Note that we still use {\em Psi-Reduction} but now just on vectors.  
We start by analyzing the shape of the result in conjunction with the indicies involved
in the computation and observe that the indices for $j$ and $k$ are contiguous allowing
us to only use the primary axis index in the mapping.
Thus, let Y denote $(<2-i> \psi A ) \times ( <1-i> \psi A)$. Then the shape of Y, i.e.
\begin{eqnarray}
\rho Y= 1 \drop (\rho A) = 1 \drop <3\;5\;4> = <5\;4>
\end{eqnarray}
i.e. the bounds for $j$ and $k$  above.
Continuing with the PCT to create the {\em generic} ONF on p=2 processors, we use the index of the primary axis, i, $\ni\;\;0 \leq  i < p$, since $\rho X = <2\;4\;5>$.
Using $\gamma_{row}$ for row major ordering, Y is transformed into:
\small
\begin{eqnarray}
a[ (( \gamma(<2-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] \nonumber \\
\times a[ (( \gamma(<1-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] 
\end{eqnarray}
Reducing, we get
\begin{eqnarray}
a[ (( \gamma(<2-i >; <3>))) \times \pi ( <5\;4>)  + \iota \pi <5\;4> ] \nonumber \\
\times a[ (( \gamma(<1-i >; <3>))) \times \pi ( <5\;4>)   )  + \iota \pi <5\;4>  ]\nonumber \\
a[( (2-i) \times  20)  + \iota 20 ] \nonumber \\
\times a[( (i-1) \times 20 )  + \iota 20 ]
\end{eqnarray}
\normalsize
which transforms the indexing into start, stride, and stop, a universal hardware description and easiliy transformed
to the mnemonics used at any hardware level ~\cite{fftharry}.

The  {\em iota} operation depicts  20 sequential 
accesses. If we wanted to map these operations to other than  scalar registers
we could conceptually add more dimensions to analyze prefetching, buffer sizes, vector registers, caches, etc.
Suppose in this example we have two vector registers to do the addition, both with length 4, we could
abstract this operation into a 5 by 4 where we can now analyze the cost of 5 vector register loads and
stores and determine if that is more cost effective than 20 scalar operations. Thus prior to code generation we
{\em could} analyze which menomnic to map to from the ONF.
